Hybrid platforms and bargaining power

### 2023-03-25 src/paper/application.tex
Do not ebbreviate references
Add figure to application section

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}

@@

\crefname{assumption}{assumption}{assumptions}
\crefname{assumption}{Assumption}{Assumptions}
\crefname{observation}{observation}{observations}
\Crefname{observation}{Observation}{Observations}

@@

@@

As in \cref{sec:model}, assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
For this service, the platform can charge a lump-sum entry fee $F_F$ to each fringe firm.\footnote{
    This is a critical difference from \textcite[]{anderson2021hybrid}, where the platform charges a per-unit royalty.
    % TODO: elaborate on this
}
In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
    This essentially means that I assume a one-sided platform, without the usual strong network effects.
    % TODO: see if I can relax this assumption
}

@@

Let us call $p_{Ti}$ the net value of product $i$.
As one would expect, demand is increasing in this net value, and decreasing in the competitors' net 
Furthermore, demand for each product is increasing in $\mu$, which can be thought of as the degree of product differentiation or the importance of taste shocks.
Finally, notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
This last property makes the optimal prices and profits of the producers very simple, as shown in the next proposition.
% \begin{align}
%     \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
%     \label{eq:variable_profit}
% \end{align}
\begin{proposition}
    The profit maximizing price for prouct $Ti$ is
    \begin{align*}
        p^*_{Ti} = c_T + \mu,
    \end{align*}
    and the profit from selling that product is
    \begin{align}
        \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
        \label{eq:optimal_profit}
    \end{align}
\end{proposition}

@@

    Otherwise, the equilibrium size of the aggregate is
    \begin{align*}
        A = N_P V_P + 1.
    \end{align*}
\end{proposition}
Note that in the first case, the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.

@@

The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $f(N_P, N_F)$ is defined as the total profits that the platform and the entrants can achieve by selling their products.
From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
\begin{align*}
    f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
\end{align*}
This yields the following closed-form expressions for the total profits of the partcipants.
\begin{proposition}
    The platform's total profits are
    \begin{align*}
        \pi^t_P &\int_0^1 f(N_P, sN_F) \ds \\
                &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
    \end{align*}
    The total profits of the whole fringe is given by
    \begin{align*}
        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
    \end{align*}
\end{proposition}
\textcolor{red}{TODO: add an example figure}

Now let us turn to how the platform's hybridness affects product variety and consumer welfare.
Let us start by establishing some properties of the toral profit function $f(n_P, n_F)$.
\begin{lemma}
    \label{lem:profit_assumptions}
    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
    Furthermore,
    \begin{align*}
        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
    \end{align*}
\end{lemma}
Using this, \cref{prop:unique_equilibrium} gives that the equilibrium is unique.
Furthermore, \cref{cor:fringe_entry} implies that an increase in the hybridness of the platform leads to a reduction in the number of fringe firms that enter the market.

@@

>>>>

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage[noabbrev,nameinlink]{cleveref}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}

@@

\crefname{assumption}{assumption}{assumptions}
\Crefname{assumption}{Assumption}{Assumptions}
\crefname{observation}{observation}{observations}
\Crefname{observation}{Observation}{Observations}

@@

\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium

@@

As in \cref{sec:model}, assume that the sellers and the consumers can only interact through an intermediary platform, denoted by $P$.
Without the platform, the fringe firms are not able to sell their products, and thus make no profits.
For this service, the platform can charge a lump-sum entry fee $F_F$ to each fringe firm.\footnote{
    This is a critical difference from \textcite[]{anderson2021hybrid}, where the platform charges a per-unit royalty.
    % TODO: elaborate on this
}
In the baseline model, I assume that entry is free for the consumers, and they are always present on the platform, no matter the other players' entry and pricing decisions.\footnote{
    This essentially means that I assume a one-sided platform, without the usual network effects.
    % TODO: see if I can relax this assumption
}

@@

Let us call $v_T - p_{Ti}$ the net value of product $i$.
As one would expect, demand is increasing in this net value, and decreasing in the competitors' net values.
Furthermore, demand for each product is increasing in $\mu$, which can be thought of as the degree of product differentiation or the importance of taste shocks.
Finally, notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
This last property makes the optimal prices and profits of the producers very simple, as shown in the next proposition.
% \begin{align}
%     \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
%     \label{eq:variable_profit}
% \end{align}
\begin{proposition}
    The profit maximizing price for prouct $Ti$ is
    \begin{align*}
        p^*_{Ti} = c_T + \mu,
    \end{align*}
    and the profit from selling that product is
    \begin{align}
        \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
        \label{eq:optimal_profit}
    \end{align}
\end{proposition}

@@

    Otherwise, if they are sufficiently high, $N_F = 0$ and the equilibrium size of the aggregate is
    \begin{align*}
        A = N_P V_P + 1.
    \end{align*}
\end{proposition}
Note that in the first case, the size of the aggregate does not depend on the platforms' product variety or the platform's product advantage.

@@

The participants negotiate over the aggregate profits that they can achieve in the subsequent period (assuming non-collusive, monopolistic pricing, as before).
I assume that bargaining outcomes are determined according to \cref{ass:profit_sharing}, where $f(N_P, N_F)$ is defined as the total profits that the platform and the entrants can achieve by selling their products.
From \cref{eq:optimal_profit}, the total profit achieved by the platform and $N_F$ fringe firms is given by
\begin{align*}
    f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}.
\end{align*}
This yields the following closed-form expressions for the total profits of the participants.
\begin{proposition}
    The platform's total profits are
    \begin{align*}
        \pi^t_P &=\int_0^1 f(N_P, sN_F) \ds \\
                &= \mu \left[ 1 - \frac{\log \left(1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} \right].
    \end{align*}
    The total profits of the whole fringe is given by
    \begin{align*}
        \pi^t_F = \mu \left[ \frac{\log \left( 1 + \frac{N_F V_F}{N_P V_P + 1} \right)}{N_F V_F} - \frac{1}{N_P V_P + N_F V_F + 1} \right] - I_F N_F.
    \end{align*}
\end{proposition}
\textcolor{red}{TODO: add an example figure}

Now let us turn to how the platform's hybridness affects product variety and consumer welfare.
Let us start by establishing some properties of the total profit function $f(n_P, n_F)$.
\begin{lemma}
    \label{lem:profit_assumptions}
    $f(n_P, n_F)$ satisfies \cref{ass:single_crossing}.
    Furthermore,
    \begin{align*}
        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0.
    \end{align*}
\end{lemma}
Using this, \cref{prop:unique_equilibrium} gives that the equilibrium is unique.
Furthermore, \cref{cor:fringe_entry} implies that an increase in the hybridness of the platform leads to a reduction in the number of fringe firms that enter the market.

@@

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$N_F^*$},
                xmin=0, xmax=1, % adjust these values as needed
                ymin=0, ymax=1, % adjust these values as needed
                % grid=major,
                % grid style={dashed,gray!30},
                width=6cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
            \addplot[color=black,mark=none,dashed] table[x=N_P,y=N_F_cf]{\equilibrium};
        \end{axis}
    \end{tikzpicture}
    \caption{The equilibrium number of fringe firms as a function of the number of platform products.}
    \label{fig:fringe_entry_eq}
\end{figure}
